NGO analysis

### 2022-07-28 Dashboard/NGO Analysis dashboard alpha.Rmd
Spelling.

  # Data frames ================================================================
  ## creating data frame from html file-----------------------------------------
  htmldata <- reactive({
    # validating file
    validate(need(
      tools::file_ext(input$html$datapath) == "html",
      "Please upload an html file."
    ))
    # Creating data frame
    read_proff(
      input$html$datapath,
      as.character(input$start), as.character(input$end)
    )
  })

>>>>

  # Data frames ================================================================
  ## Creating data frame from html file-----------------------------------------
  htmldata <- reactive({
    # validating file
    validate(need(
      tools::file_ext(input$html$datapath) == "html",
      "Please upload an html file."
    ))
    # Creating data frame
    read_proff(
      input$html$datapath,
      as.character(input$start), as.character(input$end)
    )
  })
